### 2022-09-14 chapters/optimization/java-dir/java.tex
update
add : execution environment soa
add : java defition

\subsection{Goal}
In this section, we will investigate the following research questions:
\begin{compactenum}[\indent\bf RQ\,1:]
    %  TODO : generalize this format of Rq  to all the thesis 
    \item \emph{What is the impact of existing JVM distributions on the energy consumption of Java-based software services?}
    \item \emph{What are the relevant JVM settings that can reduce the energy consumption of a given software service?}
\end{compactenum}

To answer those research questions, we conduct an empirical study to highlight the impact of this runtime.
Figure

% \subsection{definition of the JVM}
% TODO : ADD it to the introduction to 
% \begin{figure}%[ht]
%     \centering
%     \includegraphics[width=\linewidth]{imgs/Jvm_architecture}
%     \caption{JVM architecture}
%     \label{fig:hotspot}
% \end{figure}

>>>>

\subsection{characteristics of JVM}
\begin{figure}%[ht]
    \centering
    \includegraphics[width=\linewidth]{imgs/Jvm_architecture}
    \caption{JVM architecture}
    \label{fig:JVM_architecture}
\end{figure}

Java's portability is a core design goal, which means that Java applications will work exactly the same on any operating system and on any hardware.As we see in figure~\ref{fig:JVM_architecture}, Instead of machine code, this is accomplished by compiling Java language code to an intermediate representation known as Java bytecode. Java bytecode instructions are similar to machine code, but they are executed by a JVM rather than directly on the machine. As a result, Java programs will run slower and consume more memory than C++ programs. However, Just-in-Time (JIT) compilation, which is built into the JVM, improves performance by converting bytecode to machine code at runtime. Furthermore, an automatic garbage collector (GC) is used by Java to manage memory throughout the object lifecycle and to recover memory when objects are no longer in use.

\subsection{Goal}
In this section, we will investigate the following research questions:
\begin{compactenum}[\indent\bf RQ\,1:]
    \item \emph{What is the impact of existing JVM distributions on the energy consumption of Java-based software services?}
    \item \emph{What are the relevant JVM settings that can reduce the energy consumption of a given software service?}
\end{compactenum}

To answer those research questions, we conduct an empirical study to highlight the impact of this runtime.
